Data_extractions

### 2019-01-28 Data_extractions.Rmd
minor formatting edits and typos fixed

Lets try to extract data from:
 1. Figure 2a in the paper by Weil et al. 2006: Immune challenge retards seasonal reproductive regression in rodents: evidence for terminal investment (Weil2006.pdf)
 2. Figure 2a in the paper by Sadd et al. 2006: Modulation of sexual signalling by immune challenged male mealworm beetles (Tenebrio molitor, L.): evidence for terminal investment and dishonesty (Sadd2006.pdf)

@@

Name the files as following (this makes it easy to keep track of the figures being digitised):     
001_Weil_2006_Fig2a.png    
and    
002_Sadd_2006_Fig2a.png

We need to place them in a new folder - we called it metaDigitise_figures (read more about organising your extraction directories in the "Setting up directory structures " section of https://cran.r-project.org/web/packages/metaDigitise/vignettes/metaDigitise.html).

To extract our two figures we need to provide the directory path name of the folder with the images to the metaDigise() function, for example:

@@

**QUESTION 17:**    
If we have different traits in the data set (lets say number of eggs laid and probability of next abandonment) what is the problem with the  signs of effect sizes for these traits? What should we do about this?

>>>>

Let's try to extract data from:   
 1. Figure 2a in the paper by Weil et al. 2006: Immune challenge retards seasonal reproductive regression in rodents: evidence for terminal investment (**Weil2006.pdf**)   
 2. Figure 2a in the paper by Sadd et al. 2006: Modulation of sexual signalling by immune challenged male mealworm beetles (Tenebrio molitor, L.): evidence for terminal investment and dishonesty (**Sadd2006.pdf**)

@@

Name the snapshot files as following (this makes it easy to keep track of the figures being digitised):     
**001_Weil_2006_Fig2a.png**    
and    
**002_Sadd_2006_Fig2a.png**

You have to place them in a new folder - let's call it **metaDigitise_figures** (read more about organising your extraction directories in the "Setting up directory structures " section of https://cran.r-project.org/web/packages/metaDigitise/vignettes/metaDigitise.html).

To extract our two figures we need to provide the directory path name of the folder with the images to the *metaDigise()* function, for example:

@@

**QUESTION 17:**    
If we have different traits in the data set (lets say number of eggs laid and probability of nest abandonment) what is the problem with the signs of effect sizes for these traits? What should we do about this?
